Inferring Graphics Programs from Images

### 2017-05-12 paper.tex
example synthesizer outputs
updated synthesis results
improvements to figure in order to take into account Dan's feedback

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{fit}
% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2016} with
% \usepackage[nohyperref]{icml2016} above.
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays

@@

High dimensional perceptual input may seem ill matched to the abstract
semantics of a programming language. But programs with constructs like
recursion or iteration produce a simpler \emph{execution trace} of
primitive actions; for our domain the primitive actions are drawing
commands. Our hypothesis is that the execution trace of the program is
better aligned with the perceptual input, and that the trace can act
as a kind of bridge between perception and programs. We test this
hypothesis by developing a model that learns to map from an image to
the execution trace of the graphics program that drew it.  With the
execution trace in hand, we can bring to bear techniques from the
program synthesis community to recover the latent graphics program.
\remark{This is an \emph{excellent} explanation! I would add maybe one
  more sentence / citation to elaborate on what you mean by
  `techniques from the program synthesis community', as this will be
  an unfamiliar concept to some readers, I imagine.}

We develop a hybrid architecture for inferring graphics programs.  Our
approach uses a deep neural network infer an execution trace from an image;
this network recovers primitive drawing operations such as lines, circles, or
arrows~\remark{and their parameters?}
. For added robustness, we use the deep network as a proposal
distribution for a stochastic search over execution traces.
Finally, we use techniques in the program synthesis community to
recover the program from its trace.
\remark{This paragraph is all about making things a bit more specific, so you really need more specifics about program synth here.}

Each of these three components -- the deep network, the stochastic
search, the program synthesizer -- confers its own advantages. From
the deep network, we get a very fast system that can recover plausible
execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference. Are you talking about training time, here, or...?}. From the stochastic search we get
added robustness; essentially, the stochastic search can correct
mistakes made by the deep network's proposals.  From the program
synthesizer, we get abstraction: our system recovers coordinate
transformations, for loops, and subroutines, which are useful for
downstream tasks~\remark{and can help correct some mistakes of the earlier stages?}.
\remark{I wonder if this would work even better as a bulleted list...}

@@

Figure~\ref{architecture} illustrates this architecture.  We first
pass the target image and a rendering of the trace so far to a
convolutional network. Given the features extracted by the
convolutionional network, a multilayer perceptron then predicts a
distribution over the next drawing command to add to the trace.  We
predict the drawing command token-by-token, and condition each token
both on the image features and on the previously generated tokens.
For example, the network first decides to emit the \verb|circle| token
conditioned on the image features, then it emits the $x$ coordinate of
the circle conditioned on the image features and the \verb|circle|
token, and finally it predicts the $y$ coordinate of the circle
conditioned on the image features, the \verb|circle| token, and the
$x$ coordinate.
\remark{There are some more details that are important to provide about this architecture, though possibly in an Appendix: the functional form(s) of the probability distributions over tokens, the network layer sizes, which MLPs share parameters, etc.}

@@

\begin{figure}
  \begin{tikzpicture}
  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas: render$(T)$] (canvas) at (0,-5) {};
  % draw partial image on canvas
  \draw (0.5cm,-4cm) circle (0.1875cm);
  \draw (1.2cm,-4.3) circle (0.1875cm);
  \draw (0.85cm,-4.6) circle (0.1875cm);

  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};

  \node[rotate = -90,draw,thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1cm]CNN.east) {Image features};

  \node[draw,thick,circle,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north);
  \node(l1) at ([yshift = -2cm]c1.south) {\verb|circle(|};
  \node[draw,thick,circle,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east);
  \draw[->,thick] (c1.south) -- (l1.north);
  \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=3,|};
  \draw[->,thick] (c2.south) -- (l2.north);
  \node[draw,thick,circle,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east);
  \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=14)|};
  \draw[->,thick] (c3.south) -- (l3.north);

  \draw[->,thick] (features.north) -- (c1.west);
  \draw[->,thick] (c1.east) -- (c2.west);
  \draw[->,thick] (c2.east) -- (c3.west);

@@

  \draw[->,thick,dashed] (next.west) -- node[below] {Renderer: \LaTeX} (canvas.east);

  \draw[->,thick] (canvas.east) -- ([yshift = -0.5cm]CNN.west);
  \draw[->,thick] (observation.east) -- ([yshift = 0.5cm]CNN.west);
  \draw[->,thick] (CNN.east) -- (features.south);
%  \draw[]

@@

>>>>

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{fit}

\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}

% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2016} with
% \usepackage[nohyperref]{icml2016} above.
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays

@@

High dimensional perceptual input may seem ill matched to the abstract
semantics of a programming language. But programs with constructs like
recursion or iteration produce a simpler \emph{execution trace} of
primitive actions; for our domain the primitive actions are drawing
commands. Our hypothesis is that the execution trace of the program is
better aligned with the perceptual input, and that the trace can act
as a kind of bridge between perception and programs. We test this
hypothesis by developing a model that learns to map from an image to
the execution trace of the graphics program that drew it.  With the
execution trace in hand, we can bring to bear techniques from the
program synthesis community to recover the latent graphics program.
This family of techniques, called \emph{constraint-based program synthesis}~\cite{solar2008program},
work by modeling a set of possible programs inside of a constraint solver,
like a SAT or SMT solver~\cite{de2008z3}.

%% \remark{This is an \emph{excellent} explanation! I would add maybe one
%%   more sentence / citation to elaborate on what you mean by
%%   `techniques from the program synthesis community', as this will be
%%   an unfamiliar concept to some readers, I imagine.}

We develop a hybrid architecture for inferring graphics programs.  Our
approach uses a deep neural network infer an execution trace from an
image; this network recovers primitive drawing operations such as
lines, circles, or arrows, along with their parameters. For added
robustness, we use the deep network as a proposal distribution for a
stochastic search over execution traces.  Finally, we use techniques
in the program synthesis community to recover the program from its
trace.  The program synthesizer discovers constructs like loops and
geometric operations like reflections and affine transformations.
\remark{This paragraph is all about making things a bit more specific,
  so you really need more specifics about program synth here.}

Each of these three components -- the deep network, the stochastic
search, the program synthesizer -- confers its own advantages. From
the deep network, we get a fast system that can recover plausible
execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference. Are you talking about training time, here, or...?}. From the stochastic search we get
added robustness; essentially, the stochastic search can correct
mistakes made by the deep network's proposals.  From the program
synthesizer, we get abstraction: our system recovers coordinate
transformations, for loops, and subroutines, which are useful for
downstream tasks and can help correct some mistakes of the earlier stages.
\remark{I wonder if this would work even better as a bulleted list...}

@@

Figure~\ref{architecture} illustrates this architecture.  We first
pass a $256\times 256$ target image and a rendering of the trace so
far to a convolutional network -- these two inputs are represented as
separate channels for the convnet. Given the features extracted by the
convnet, a multilayer perceptron then predicts a distribution over the
next drawing command to add to the trace.  We predict the drawing
command token-by-token, and condition each token both on the image
features and on the previously generated tokens.  For example, the
network first decides to emit the \verb|circle| token conditioned on
the image features, then it emits the $x$ coordinate of the circle
conditioned on the image features and the \verb|circle| token, and
finally it predicts the $y$ coordinate of the circle conditioned on
the image features, the \verb|circle| token, and the $x$ coordinate.
\remark{There are some more details that are important to provide
  about this architecture, though possibly in an Appendix: the
  functional form(s) of the probability distributions over tokens, the
  network layer sizes, which MLPs share parameters, etc.}

@@

\begin{figure}
  \begin{tikzpicture}
  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
  % draw partial image on canvas
  \draw (0.5cm,-4cm) circle (0.1875cm);
  \draw (1.2cm,-4.3) circle (0.1875cm);
  \draw (0.85cm,-4.6) circle (0.1875cm);

  \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigotimes$};

  \node[rotate = -90,draw,ultra thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1cm]CNN.east) {Image features};

  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north) {MLP};
  \node(l1) at ([yshift = -2cm]c1.south) {\verb|circle(|};
  \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
  \draw[->,ultra thick] (c1.south) -- (l1.north);
  \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=3,|};
  \draw[->,ultra thick] (c2.south) -- (l2.north);
  \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
  \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=14)|};
  \draw[->,ultra thick] (c3.south) -- (l3.north);

  \draw[->,ultra thick] (features.north) -- (c1.west);
  \draw[->,ultra thick] (features.north) to[out = 45,in = 90] (c2.north);
  \draw[->,ultra thick] (features.north) to[out = 70,in = 90] (c3.north);
  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c3.west);
  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- (c3.west);

@@

  \draw[->,thick,dashed] (next.west) -- (canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX};

  \draw[->,ultra thick] (canvas.east) -- (tensorProduct.south);%[yshift = -0.5cm]CNN.west);
  \draw[->,ultra thick] (observation.east) -- (tensorProduct.north);%([yshift = 0.5cm]CNN.west);
  \draw[->,ultra thick] (tensorProduct.east)  -- node[center,fill = white,rotate = 90] {{\tiny $256\times 256\times 2$}}  (CNN.west);
  \draw[->,ultra thick] (CNN.east) -- node[center,fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}} (features.south);
%  \draw[]

@@

  \pagebreak
  \section{Preliminary Synthesis results} 
\input{synthesizerOutputs.tex}
